{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-26 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

\section{Preliminaries}\label{sec:preliminaries}
    Throughout the writing, let the ambient space is $\RR^n$. 
    The optimization problem is
    \begin{align*}
        \min_{x \in \RR^n} F(x). 
    \end{align*}
    This section introduces the Nesterov's estimating sequence technique. 
    This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
    Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating squence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate. 
    \subsection{Nesterov's Estimating Sequence}
        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
            Let $(\phi_k : \RR^n \rightarrow\RR)_{k \ge 0}$ be a sequence of functions. 
            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
            \begin{enumerate}
                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k(x)$. 
                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
            \end{enumerate}
        \end{definition}
        \begin{observation} 
            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
            Then observe that $\forall k \ge 0$:  
            \begin{align*}
                \Delta_k(x) 
                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
                \\
                x = x_k\implies 
                \Delta_k(x_k) 
                &\ge 
                \phi_k^* - F(x_k) \ge 0
                \\
                x = x_* \implies 
                \Delta_k(x_*)
                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0
            \end{align*}
            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
            \begin{align*}
                \phi_{k + 1}(x) - \phi_k(x) 
                &\le - \alpha_k (\phi_k(x) - F(x))
                \\
                \iff 
                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                &\le 
                -\alpha_k(\phi_k(x) - F(x))
                \\
                \iff
                \Delta_{k + 1}(x) - \Delta_k(x) &\le
                - \alpha_k\Delta_k(x)
                \\
                \iff 
                \Delta_{k + 1}(x) 
                &\le 
                (1 - \alpha_k)\Delta_k(x). 
            \end{align*}
            Unrolling the above recursion it yields: 
            \begin{align*}
                \Delta_{k + 1}(x) &\le 
                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
                \left(
                    \prod_{i = 0}^k(1 - \alpha_i)
                \right)\Delta_0(x). 
            \end{align*}
            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
            $$
                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
            $$ 
        \end{observation}
        Creativity is important in the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.

@@

            \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}

@@

        For a detailed proof of the estimating sequence with comparison to the accelerated proximal gradient method, see Appendix \ref*{sec:app:exct-acc-ppm}. 

@@

    For the inexact evaluation of PPM, Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text which is the following: 

@@

\section{Lin 2015}\label{sec:lin-2015}
    The section introduces the Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 
    We warn the readers about the followings: 
    \begin{enumerate}
        \item The proofs in HongZhou Lin's original paper of Universal Catalyst is depressingly long and complicated. It is a result of using the constructive approach of Nesterov's estimating sequence. 
        \item Controlling the errors of inexact proximal point evaluations is context specific. Lin hinted at ways to track the errors such as using duality and non-negativity assumption of the objective. He illustrated the use of the meta acceleration on their own method called: ``Accelerated MISO-Prox", in general there is not a universal solution. 
        \item We will provide proofs to clarify some of their proofs and compare with existing proofs and drawing references in the literatures in the appendix. 
    \end{enumerate}
    Let's assume $F$ is a $\mu \ge 0$ strongly convex function. 
    Throughout this section we make the following notations
    \begin{align*}
        \mathcal M^{\kappa^{-1}}(x; y) &:= F(x) + \frac{\kappa}{2}\Vert x - y\Vert^2, 
        \\
        \mathcal J_{\kappa^{-1}} y &:= \argmin_x \mathcal M^{\kappa^{-1}} (x, y). 
    \end{align*}
    Their algorithm is almost exactly the same as Nesterov's 2.2.20 \cite{nesterov_lectures_2018} which we stated in the definition below: 
    \begin{definition}[Lin's accelerated proximal point method]
        Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa$ and $\alpha_0$. 
        Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
        Initialize $x_0 = y_0$, then the algorithm generates $(x_k, y_k)$ satisfies for all $k \ge 1$
        \begin{align*}
            & \text{find } x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1} \text{ such that } \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}, y_{k - 1}) \le \epsilon_k
            \\
            & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa)) 
            \\
            & 
            y_{k} = x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}(x_k - x_{k - 1}). 
        \end{align*}
    \end{definition}
    \begin{remark}
        The algorithm is similarity to
        \hyperref[def:nes-est-seq-pg]{Definition \ref*{def:nes-est-seq-pg}}. 
        In contrast, it has an inexact proximal point step controlled by $\epsilon_k$, and the Lipschitz constant $L$ is absent instead it has $\kappa + \mu$. 
        Evaluating $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ is also possible because the function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ is strongly convex, hence its optimality gap can be bounded via trackable quantity $\partial \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1})$.

@@

    For theoretical interests, there is a major difference between Lin's approach and Guler's approach. 
    Lin didn't formulate any of the intractable quantities in the definitions for his Nesterov's estimating sequence $\phi_k$. 
    One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015}. 
    The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.

    \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
        Let $F$ be a $\mu\ge 0$ strongly convex and fix $\kappa$. 
        If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$, then it has for all $x$: 
        \begin{align*}
            F(x) &\ge 
            F(x_k) + \kappa \langle y_{k - 1} - x_k, x - x_k\rangle
            + \frac{\mu}{2}\Vert x - x_k\Vert^2 
            + (\kappa + \mu)\langle  x_k - x_k^*, x - x_k\rangle 
            - \epsilon_k.
        \end{align*}
    \end{lemma}
    \begin{remark}
        The lemma plays a key role because it allows Lin to denote his Nesterov's estimating sequence to be for all $k \ge0$: 
        \begin{align*}
            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x)
            + \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k \rangle
                + \frac{\mu}{2}\Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        It is void of intractable quantities. 
    \end{remark}

@@

    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]\label{thm:canon-prox-grad-est-seq}
        \; \\
        Denote $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
        \begin{align*}
            & g_k := L(y_k - \widetilde{\mathcal J}_{L^{-1}} y_k),
            \\
            & l_F(x; y_k) := 
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \langle g_k, x - y_k\rangle 
                + \frac{1}{2L}\Vert g_k\Vert^2, 
            \\
            & \alpha_k \in (0, 1),
            \\
            & 
            \phi_{k + 1}(x)
            := (1 - \alpha_k)\phi_k (x) + 
            \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2), 
        \end{align*}
        where $(y_k)_{k\ge 0}$ any sequence. 
        If we define the canonical form for $\phi_k$ as convex quadratic parameterized by positive sequence $(\gamma_k), \phi_k^*$:  
        \begin{align*}
            \phi_k(x) &:= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2, 
        \end{align*}
        where $\phi_k^* := \min_{x} \phi_k(x)$. 
        Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$: 
        {\small
        \begin{align*}      
            \gamma_{k + 1} &= (1 - \alpha_k) \gamma_k + \mu \alpha_k,
            \\
            v_{k + 1} &= \gamma_{k + 1}^{-1}
            (\gamma_k(1 - \alpha_k)v_k - \alpha_k g_k + \mu \alpha_k y_k),
            \\
            \phi_{k + 1}^* &= 
            (1 - \alpha_k)\phi_k^*
            + \alpha_k\left(
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \frac{1}{2L}\Vert g_k\Vert^2 
            \right) 
            \\
                &\quad 
                - \frac{\alpha_k^2}{2 \gamma_{k + 1}} \Vert g_k\Vert^2 
                + 
                \frac{\alpha_k(1 - \alpha_k)\gamma_k}{\gamma_{k + 1}} 
                \left(
                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2 
                    + \langle v_k - y_k , g_k\rangle
                \right). 
        \end{align*}
        }
    \end{theorem}

@@

                & \textcolor{gray}{
                    A_{k + 1} = (1 - \alpha_k)A_k

@@

@@

    \subsection{Inexact proximal inequality}

@@

    \subsection{Approximated Nesterov's Estimating sequence}
        In this subsection, let $\phi_k$ be the Nesterov's estimating sequence for Catalyst. 
        For all $k \ge0$, $\phi_k$ satisfies 
        \begin{align*}
            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x) + 
            \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k\rangle
                + \frac{\mu}{2} \Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        Observe that $\phi_k$ is a simple quadratic function. 
        We prove following theorem which is Lemma A.6 in Lin's writings on Catalyst \cite{lin_universal_2015}. 
        \begin{theorem}[Canonical form of Catalyst estimating sequence]\;\\
            Define $v_k, \gamma_k$ to be the parameters for the canonical form of $\phi_k$ as given by 
            \begin{align*}
                \phi_k(x) &= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2, 
            \end{align*}
            where $\phi_k^* = \min_x \phi_k(x)$. 
            Then the parameters of the canonical form $(\gamma_{k})_{k \ge0}, (v_k)_{k \ge 0}, (\phi_k^*)_{k\ge 0}$ satisfies for all $k \ge 1$: 
            \begin{align*}
                \gamma_k &= (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu, 
                \\
                v_k &= 
                \gamma_k^{-1}(
                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
                    + \alpha_{k - 1}\mu x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
                ), 
                \\
                \phi_k^* &= (1 - \alpha_{k - 1})\phi_{k - 1}^*
                + \alpha_{k - 1}F(x_k)
                - \frac{\alpha_{k - 1}^2}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
                \\
                &\quad 
                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                \left(
                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2 + 
                    \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
                \right). 
            \end{align*}
        \end{theorem}
        \begin{proof}
            For $v_{k + 1}$, solve for $\nabla \phi_k(v_k) = \mathbf 0$ using the recursive definition. 
            For $\gamma_k$, consider the Hessian $\nabla^2 \phi_k$ using the recursive definition. 
            The process is similar to derivations in 
            \hyperref[app:sec:thm-claim-acc-prox-grad]{Section \ref*{app:sec:thm-claim-acc-prox-grad}}.

@@

    \subsection{Controlling the errors}

>>>>

\section{Preliminaries}\label{sec:preliminaries}
    Throughout the writing, let the ambient space is $\RR^n$. 
    The optimization problem is
    \begin{align*}
        \min_{x \in \RR^n} F(x). 
    \end{align*}
    This section introduces the Nesterov's estimating sequence technique. 
    This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
    Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating sequence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate. 
    \subsection{Nesterov's Estimating Sequence}
        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
            Let $(\phi_k : \RR^n \rightarrow\RR)_{k \ge 0}$ be a sequence of functions. 
            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
            \begin{enumerate}
                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k(x)$. 
                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
            \end{enumerate}
        \end{definition}
        \begin{observation} 
            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
            Then observe that $\forall k \ge 0$:  
            \begin{align*}
                \Delta_k(x) 
                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
                \\
                x = x_k\implies 
                \Delta_k(x_k) 
                &\ge 
                \phi_k^* - F(x_k) \ge 0;
                \\
                x = x_* \implies 
                \Delta_k(x_*)
                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0. 
            \end{align*}
            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
            \begin{align*}
                \phi_{k + 1}(x) - \phi_k(x) 
                &\le - \alpha_k (\phi_k(x) - F(x))
                \\
                \iff 
                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                &\le 
                -\alpha_k(\phi_k(x) - F(x))
                \\
                \iff
                \Delta_{k + 1}(x) - \Delta_k(x) &\le
                - \alpha_k\Delta_k(x)
                \\
                \iff 
                \Delta_{k + 1}(x) 
                &\le 
                (1 - \alpha_k)\Delta_k(x). 
            \end{align*}
            Unrolling the above recursion it yields: 
            \begin{align*}
                \Delta_{k + 1}(x) &\le 
                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
                \left(
                    \prod_{i = 0}^k(1 - \alpha_i)
                \right)\Delta_0(x). 
            \end{align*}
            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
            $$
                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
            $$ 
        \end{observation}
        Creativity is important in the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.

@@

            \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}, 

@@

        For a detailed proof of the estimating sequence with comparison to the accelerated proximal gradient method, see 
        \hyperref[sec:app:exct-acc-ppm]{Appendix \ref*{sec:app:exct-acc-ppm}}. 

@@

    Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text for inexact proximal evaluation: 

@@

\section{Lin's Estimating Sequence}\label{sec:lin-2015}
    The section introduces the Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 
    We warn the readers about the followings: 
    \begin{enumerate}
        \item The proofs in HongZhou Lin's original paper of Universal Catalyst is depressingly long and complicated. It is a result of using the constructive approach of Nesterov's estimating sequence. 
        \item Controlling the errors of inexact proximal point evaluations is context specific. Lin hinted at ways to track the errors such as using duality and non-negativity assumption of the objective. He illustrated the use of the meta acceleration on their own method called: ``Accelerated MISO-Prox", in general there is not a universal solution. 
        \item We will provide proofs to clarify some of their proofs and compare with existing proofs and drawing references in the literatures in the appendix. 
    \end{enumerate}
    Let's assume $F$ is a $\mu \ge 0$ strongly convex function. 
    Throughout this section we make the following notations
    \begin{align*}
        \mathcal M^{\kappa^{-1}}(x; y) &:= F(x) + \frac{\kappa}{2}\Vert x - y\Vert^2, 
        \\
        \mathcal J_{\kappa^{-1}} y &:= \argmin_x \mathcal M^{\kappa^{-1}} (x, y). 
    \end{align*}
    Their algorithm is almost exactly the same as Nesterov's 2.2.20 \cite{nesterov_lectures_2018} which we stated in the definition below: 
    \begin{definition}[Lin's accelerated proximal point method]
        Define the estimating sequence $(\phi_k)_{k \ge0}$ recursively by: 
        \begin{align*}
            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x)
            + \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k \rangle
                + \frac{\mu}{2}\Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa$ and $\alpha_0$. 
        Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
        Initialize $x_0 = y_0$, then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
        \begin{align*}
            & \text{find } x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1} \text{ such that } \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}, y_{k - 1}) \le \epsilon_k
            \\
            & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa)) 
            \\
            & 
            y_{k} = x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}(x_k - x_{k - 1}). 
        \end{align*}
    \end{definition}
    \begin{remark}
        The algorithm is similarity to
        \hyperref[def:nes-est-seq-pg]{Definition \ref*{def:nes-est-seq-pg}}. 
        In contrast, it has an inexact proximal point step controlled by $\epsilon_k$, and the Lipschitz constant $L$ is absent instead it has $\kappa + \mu$. 
        Evaluating $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ is also possible because the function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ is strongly convex, hence its optimality gap can be bounded via trackable quantity $\partial \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1})$.

@@

    For theoretical interests, there is a major difference between Lin's approach and Guler's approach. 
    Lin didn't formulate any of the intractable quantities in the definitions for his Nesterov's estimating sequence $\phi_k$. 
    One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015} which is stated below. 
    The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.

    \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
        Let $F$ be a $\mu\ge 0$ strongly convex and fix $\kappa$. 
        If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$, then it has for all $x$: 
        \begin{align*}
            F(x) &\ge 
            F(x_k) + \kappa \langle y_{k - 1} - x_k, x - x_k\rangle
            + \frac{\mu}{2}\Vert x - x_k\Vert^2 
            + (\kappa + \mu)\langle  x_k - x_k^*, x - x_k\rangle 
            - \epsilon_k.
        \end{align*}
    \end{lemma}
    \begin{remark}
        For a detailed proof of the lemma, see 
        \hyperref[app:sec:inxct-pg-ineq]{Appendix\ref*{app:sec:inxct-pg-ineq}}.

    \end{remark}
    Using this inexact proximal inequality, we showed the proof of Lemma A.8 in Lin's paper \cite{lin_universal_2015} in 
    \hyperref[app:sec:appx-nes-est-seq]{Appendix \ref*{app:sec:appx-nes-est-seq}}
    and 
    \hyperref[app:sec:appx-nes-seq-errs-ctrl]{Appendix \ref*{app:sec:appx-nes-seq-errs-ctrl}}. 
    These result construct the Nesterov's estimating sequence by rolling up the error in the recurrence while avoiding intractable quantities appearing in the algorithm.

@@

    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]\label{thm:canon-prox-grad-est-seq}
        \; \\
        Fix any $x_0 \in \RR^n$ to, 
        define $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
        \begin{align*}
            & g_k := L(y_k - \widetilde{\mathcal J}_{L^{-1}} y_k),
            \\
            & l_F(x; y_k) := 
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \langle g_k, x - y_k\rangle 
                + \frac{1}{2L}\Vert g_k\Vert^2, 
            \\
            & \alpha_k \in (0, 1),
            \\
            & 
            \phi_{k + 1}(x)
            := (1 - \alpha_k)\phi_k (x) + 
            \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2), 
        \end{align*}
        where $(y_k)_{k\ge 0}$ any sequence. 
        If we define the canonical form for $\phi_k$ as convex quadratic parameterized by positive sequence $(\gamma_k), \phi_k^*$:  
        \begin{align*}
            \phi_k(x) &:= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2, 
        \end{align*}
        where $\phi_k^* := \min_{x} \phi_k(x)$, $\gamma_0 > 0$ and $x_0 = v_0$. 
        Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$: 
        {\small
        \begin{align*}      
            \gamma_{k + 1} &= (1 - \alpha_k) \gamma_k + \mu \alpha_k,
            \\
            v_{k + 1} &= \gamma_{k + 1}^{-1}
            (\gamma_k(1 - \alpha_k)v_k - \alpha_k g_k + \mu \alpha_k y_k),
            \\
            \phi_{k + 1}^* &= 
            (1 - \alpha_k)\phi_k^*
            + \alpha_k\left(
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \frac{1}{2L}\Vert g_k\Vert^2 
            \right) 
            \\
                &\quad 
                - \frac{\alpha_k^2}{2 \gamma_{k + 1}} \Vert g_k\Vert^2 
                + 
                \frac{\alpha_k(1 - \alpha_k)\gamma_k}{\gamma_{k + 1}} 
                \left(
                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2 
                    + \langle v_k - y_k , g_k\rangle
                \right). 
        \end{align*}
        }
    \end{theorem}

@@

@@

            Equality $A_{k + 1} = (1 - \alpha_k)A_k$ is used on the second last inequality for the above. 

@@

    \subsection{Inexact proximal inequality}\label{app:sec:inxct-pg-ineq}

@@

    \subsection{Approximated Nesterov's Estimating sequence}\label{app:sec:appx-nes-est-seq}
        In this subsection, let $\phi_k$ be the Nesterov's estimating sequence for Catalyst. 
        For all $k \ge0$, $\phi_k$ satisfies 
        \begin{align*}
            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x) + 
            \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k\rangle
                + \frac{\mu}{2} \Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        Observe that $\phi_k$ is a simple quadratic function. 
        We prove following theorem which is Lemma A.6 in Lin's writings on Catalyst \cite{lin_universal_2015}. 
        \begin{theorem}[Canonical form of Catalyst estimating sequence]\;\\
            Define $v_k, \gamma_k$ to be the parameters for the canonical form of $\phi_k$ as given by 
            \begin{align*}
                \phi_k(x) &= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2, 
            \end{align*}
            where $\phi_k^* = \min_x \phi_k(x)$. 
            Then the parameters of the canonical form $(\gamma_{k})_{k \ge0}, (v_k)_{k \ge 0}, (\phi_k^*)_{k\ge 0}$ satisfies for all $k \ge 1$: 
            \begin{align*}
                \gamma_k &= (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu, 
                \\
                v_k &= 
                \gamma_k^{-1}(
                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
                    + \alpha_{k - 1}\mu x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
                ), 
                \\
                \phi_k^* &= (1 - \alpha_{k - 1})\phi_{k - 1}^*
                + \alpha_{k - 1}F(x_k)
                - \frac{\alpha_{k - 1}^2}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
                \\
                &\quad 
                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                \left(
                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2 + 
                    \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
                \right). 
            \end{align*}
        \end{theorem}
        \begin{proof}
            For $v_{k + 1}$, solve for $\nabla \phi_k(v_k) = \mathbf 0$ using the recursive definition. 
            For $\gamma_k$, consider the Hessian $\nabla^2 \phi_k$ using the recursive definition. 
            The process is similar to derivations in 
            \hyperref[app:sec:thm-claim-acc-prox-grad]{Section \ref*{app:sec:thm-claim-acc-prox-grad}}.

@@

    \subsection{Controlling the errors}\label{app:sec:appx-nes-seq-errs-ctrl}
